Security Metrics for the Android Ecosystem

### 2015-07-24 spsm04-thomas.tex
Tweaks

\begin{abstract}
The security of Android depends on security updates for critical vulnerabilities being shipped to devices.
We define the FUM security metric to rank the performance of device manufacturers and network operators, based on their provision of updates and exposure to critical vulnerabilities.
Using a corpus of \daNumOSDevices\ devices we show that there is significant variability in the timely delivery of security updates across different device manufacturers and network operators.
This provides a comparison point for purchasers to determine which device manufacturers and network operators to use.
We argue that publishing metrics like this provides an important incentive to manufacturers and operators to ship security updates.
This is the first paper to quantify security update performance of device manufacturers and network operators.
\todo{Do we want to pull numeric results into the abstract or leave them out to emphasise the method rather than the results?}
\end{abstract}

@@

The Android update process is slow because its development is distributed among many parties and has a long multi-stage pipeline~\cite{HTC2013}.
The security of Android relies on many open source projects, including the Li\-nux kernel, Open\-SSL and Bouncy\-Castle, as well as Google, who build the core platform.
In addition, device manufacturers (we know of \daNumManufacturers\footnote{\label{foot:dadata}We computed this from the \da~\cite{Wagner2013} data, see \S\ref{sec:android_update_process}.}) and network operators (\daNumOperators\dafoot) may make further modifications before devices are shipped to customers.
Understanding this ecosystem is important because device manufacturers have introduced additional vulnerabilities in the past~\cite{Grace2012}.
The cause of the slow update process could be: upstream open source projects releasing patches slowly, Google including them slowly, manufacturers including them slowly, network operators shipping them slowly or customers not installing them.
We present a better understanding of both the ecosystem of Android development and associated vulnerabilities more fully in~\S\ref{sec:android_ecosystem}.

>>>>

\begin{abstract}
The security of Android depends on timely delivery of security updates for critical vulnerabilities .
We define the FUM security metric to rank the performance of device manufacturers and network operators, based on their provision of updates and exposure to critical vulnerabilities.
Using a corpus of \daNumOSDevices\ devices we show that there is significant variability in the timely delivery of security updates across different device manufacturers and network operators.
This provides a comparison point for purchasers to determine which device manufacturers and network operators to use.
We argue that publishing metrics like this provides an important incentive to manufacturers and operators to ship security updates.
This is the first paper to quantify security update performance of device manufacturers and network operators.
\todo{Do we want to pull numeric results into the abstract or leave them out to emphasise the method rather than the results?}
\end{abstract}

@@

The Android update process is slow because its development is distributed among many parties and has a long multi-stage pipeline~\cite{HTC2013}.
The security of Android relies on many open source projects, including the Li\-nux kernel, Open\-SSL and Bouncy\-Castle, as well as Google, who build the core platform.
In addition, device manufacturers (we know of \daNumManufacturers) and network operators (\daNumOperators) may make further modifications before devices are shipped to customers.
Understanding this ecosystem is important because device manufacturers have introduced additional vulnerabilities in the past~\cite{Grace2012}.
The cause of the slow update process could be: upstream open source projects releasing patches slowly, Google including them slowly, manufacturers including them slowly, network operators shipping them slowly or customers not installing them.
We present a better understanding of both the ecosystem of Android development and associated vulnerabilities more fully in~\S\ref{sec:android_ecosystem}.
